EWJN from a BCS Superconductor

### 2021-02-05 paper.tex
Adds figures for the dielectric functions

@@

\newcommand{\vf}{v_{\mathrm{F}}}

@@

>>>>

\usepackage{cleveref}

@@

\newcommand{\vf}{v_{\mathrm{F}}}
\newcommand{\qf}{q_{\mathrm{F}}}

@@

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{Cond1Re}
	\caption{$\Re[\epsilon(q)]$ for $\omega = 1$, $\tau = 0.5$, $\omega_p = 10$, $\vf = 1$, $T = .9999 T_c$, $T_c = 3$} \label{fig:cond1Re}
\end{figure}

\begin{figure}[htp]
	\centering
	\includegraphics[width=12cm]{Cond1Im}
	\caption{$\Im[\epsilon(q)]$ for $\omega = 1$, $\tau = 0.5$, $\omega_p = 10$, $\vf = 1$, $T = .9999 T_c$, $T_c = 3$} \label{fig:cond1Im}
\end{figure}

The Lindhard and Nam dielectric constants are compared in \cref{fig:cond1Re} and \cref{fig:cond1Im}, plotting the real and imaginary part for small representative values.
In this regime, $\omega_p > T_c > \omega$, as is typical for the frequency regime of interest, while $\tau$ is chosen to be smaller than $\omega$.
For a typical metal in this description, the Fermi wavevector $\qf$ is around the same order as $\sqrt{3}\frac{\omega_p}{\vf}$ (see discussion on this point in Solyom\cite{SolyomV3}).
We can see in \cref{fig:cond1Im} that the Lindhard dielectric function goes to zero for $q < \qf \approx 10 \sqrt{3}$.
